### 2021-02-18 text/draft.tex
histogram

\texttt{\_Keywords.clean\_keywords} is the implementation the parser and
the recursive cleaner is implemented by
\texttt{\_Keywords.clean\_keyword}. To create the desired list of clean
keywords, saved as \texttt{keywords/keywords\_clean.json}, we call
\texttt{\_Keywords.clean\_keywords} with the extracted keywords as
argument:

@@

!! Frequency

!! Cumulative sum histogram

\begin{figure}
\centering
\includegraphics{images/keywords_clean_histogram_a.pdf}
\caption{Bla.}
\end{figure}

\begin{figure}
\centering
\includegraphics{images/keywords_clean_histogram_b.pdf}
\caption{Bla.}
\end{figure}

@@

>>>>

\texttt{\_Keywords.clean\_keywords} is the implementation the parser
while the recursive cleaner is implemented by
\texttt{\_Keywords.clean\_keyword}. To create the desired list of clean
keywords, saved as \texttt{keywords/keywords\_clean.json}, we call
\texttt{\_Keywords.clean\_keywords} with the extracted keywords as
argument:

@@

\texttt{keywords/keywords\_clean.json} has 36'901 entries many of which
are duplicates. We hence deduplicate and count the number of occurrences
of each keyword. This is achieved by calling
\texttt{\_Keywords.make\_histogram} on
\texttt{keywords/keywords\_clean.json} and saving the output as
\texttt{keywords/keywords\_clean\_histogram.json}:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{keywords\_clean }\OperatorTok{=}\NormalTok{ \_Utility.load\_json(DIR }\OperatorTok{+} \StringTok{"/keywords/keywords\_clean.json"}\NormalTok{)}
\NormalTok{keywords\_histogram }\OperatorTok{=}\NormalTok{ \_Keywords.make\_histogram(keywords\_clean)}
\NormalTok{\_Utility.save\_json(keywords\_histogram, DIR }\OperatorTok{+} \StringTok{"keywords/keywords\_clean\_histogram.json"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

An analysis of \texttt{keywords/keywords\_clean\_histogram.json} shows
that the distribution of keywords is strongly skewed right but that (see
Figure 3 for details).

\begin{figure}
\centering
\includegraphics{images/keywords_clean_histogram_abc.pdf}
\caption{In \texttt{keywords/keywords\_clean\_histogram.json}, the
distribution of keywords is strongly skewed right
(\(min = Q1 = M = Q3 = 1\) and \(max = 910\)). However, even though
keywords with only one occurrence constitute over 75\% of the total
keywords, they constitute less than 35\% of the total occurrences. The
most common keywords with 50 or more occurrences are extreme outliers
but make up almost 20\% of the total occurrences.}
\end{figure}

@@

As explained in section X, Annif assigns index terms from a controlled
vocabulary. If we want to assess the quality of the indexing via a gold
standard, we must therefore ensure that the gold standard makes use of
the vocabulary used by Annif. As seen in section Y, the relevant
(English) vocabularies are Wikidata YSO. The next step in constructing
the native gold standard is hence to reconcile the extracted and cleaned
keywords with YSO and Wikidata.

The tool of choice for reconciliation is OpenRefine (see
\protect\hyperlink{openrefine}{section OpenRefine}). We import
\texttt{keywords/keywords\_clean\_histogram.json} as a new project.

Before we do so, let us briefly look at the data in
\texttt{keywords/keywords\_clean.json}.

for a given input text, Annif assigns index terms from some controlled
vocabulary. Any gold standard employed to assess the quality of this
indexing must therefore make use of the same controlled vocabulary.
